### 2011-01-31 trunk/papers/webist2011/paper_ssec_discovery.tex
squeezing things to get down to 6 pages - done
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1224 d8b0c59b-6544-0410-94d9-83a5658a058e

In artificial intelligence, the term \emph{planning} originally meant to search for a sequence of logical operators or actions that transform an initial state into a desired goal state.% Presently, it also includes many decision-theoretic ideas, imperfect state information, and game-theoretic equilibria.

>>>>

% In artificial intelligence, the term \emph{planning} originally meant to search for a sequence of logical operators or actions that transform an initial state into a desired goal state.% Presently, it also includes many decision-theoretic ideas, imperfect state information, and game-theoretic equilibria.
